Future Virtual Particle Method for Pedestrian Navigation

### 2014-12-07 doc/informe/paper.tex
agrego secciones habladas con daniel en la ultima reunion. correciones varias.

\subsection{Definition}

@@

Fig 1: Pedestrian and his FVP.

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{pedestrian-top}\protect\caption{Pedestrian top view}
\end{figure}

In the document, we will call pedestrians with a letter and FVP of
pedestrian x will be called x'.\\

\subsection{Algorithm}

@@

The pedestrian movement is calculated in four steps:
\begin{enumerate}
\item Calculate forces for each FVP.
\item Update positions for each FVP.
\item Calculate forces for each pedestrian.
\item Update positions for each pedestrian.\\

\end{enumerate}
Each step is defined as follows:
\begin{enumerate}
\item FVP force calculation.

For each pedestrian $i$, the force that his future $i'$ will suffer
is calculated in this step. The magnitude of this force will depend
on two factors: by each of the other pedestrians and the walls that
might exists surronding $i$. The final value of the force applied
over the future $i'$ will be the addition of the latest two factors.

The fist factor is caluclated for each of the pedestrian $j$ ($j\neq i$).
First, we filter all pedestrians who are not in the range of sight
of pedestrian $i$. This condition is verified using the following
formula:

\[
\overrightarrow{ii'}\bullet\overrightarrow{ij'}<0
\]

This filter is represents the fact that a pedestrian (in most cases)
is not aware of what each of the pedestrians that are behind him are
doing. Hence, they are ignored. Once filtered, the pedestrian will
try to face towards the direction that think is best for avoiding
all the obstacles. This factor is represented using the social force
formula from Helbing's model.

@@

Figure 2.2 shows the external forces that a pedestrian $i$ suffers
because of another pedestrian ($j$) and also the direction in wich
$i$ desires to move.

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{pedestrian-top-forces}\protect\caption{External forces affecting future $i'$}
\end{figure}

@@

After this, the final $F_{i'}$ is computed by adding all the terms.
$F_{i'}=F_{ext}(i)+F_{i\, s1}+F_{i\, s2}$

\item FVP position update.

In this stage, the position of the FVP is updated with Euler's formula
and the forces calculated in the previous step.

@@

At last, we find $F'_{i'}=F_{i'}+FL_{i'}+FA_{i'}$ and apply euler's
movement equations.

\end{itemize}
\item Pedestrian forces calculation.

The pedestrian always wants to move in the direction his FVP is pointing
and its magnitude is defined as Fd or desire force:

@@

\item Pedestrian position update.

The new position of the pedestrian will be calculated using Euler's
formula and the desire force calculated in the previous step.

@@

\begin{table}[H]
{\scriptsize{}}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
{\scriptsize{}Values} & {\scriptsize{}1} & {\scriptsize{}2} & {\scriptsize{}3} & {\scriptsize{}4} & {\scriptsize{}5} & {\scriptsize{}6}\tabularnewline
\hline 
\hline 
{\scriptsize{}$\alpha=800,\,\beta=[0.65,\,0.85]$} & {\scriptsize{}(1.800, 0.748) } & {\scriptsize{}(34.600, 8.333) } & {\scriptsize{}(1.024, 0.016) } & {\scriptsize{}(1.910, 0.022) } & {\scriptsize{}(2.392, 0.005) } & {\scriptsize{}(111.062, 19.122)}\tabularnewline
\hline 
{\scriptsize{}$\alpha=2000,\,\beta=0.08$} & {\scriptsize{}(5.333, 2.625)} & {\scriptsize{}(12.333, 8.340) } & {\scriptsize{}(1.052, 0.003) } & {\scriptsize{}(1.876, 0.003) } & {\scriptsize{}(2.391, 0.002) } & {\scriptsize{}(106.185, 13.778)}\tabularnewline
\hline 
\end{tabular}\protect\caption{Metrics comparing SFM vs FVPM. Average of $10$ runs.}
\end{table}

>>>>

\subsection{Geometrical definition}

@@

Figure \ref{fig:Pedestrian-top-view} shows a pedestrian geomtrical
definition:

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{pedestrian-top}\protect\caption{\label{fig:Pedestrian-top-view}Pedestrian top view}
\end{figure}

Figure \ref{fig:Pedestrian-vectors} shows all the vectorial definition
that will be used:

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{geometry}\protect\caption{\label{fig:Pedestrian-vectors}Vectorial definitions}
\end{figure}

\subsection{Dynamics of the FPV Model}

@@

Each step is defined as follows:

\subsubsection{Forces}
\begin{itemize}
\item Dyamic of the FVP

For each pedestrian $i$, the force that his future $i'$ will suffer
is calculated in this step. The magnitude of this force is calculated
using two factors:

The fist factor is caluclated for each of the pedestrian $j$ ($j\neq i$)
who is in the range of sight of pedestrian $i$. This restriction
is verified using the following condition:

\[
\mathbf{r_{ii'}}\bullet\mathbf{r_{ij'}}<0
\]

This filter is represents the fact that a pedestrian (in most cases)
is not aware of what each of the pedestrians that are behind him are
doing. Hence, they are ignored. The formula for

@@

Figure \ref{fig:External-forces-affecting} shows the external forces
that a pedestrian $i$ suffers because of another pedestrian ($j$)
and also the direction in wich $i$ desires to move.

\begin{figure}[H]
\centering{}\includegraphics[scale=0.5]{pedestrian-top-forces}\protect\caption{\label{fig:External-forces-affecting}External forces affecting future
$i'$}
\end{figure}

@@

After this, the final $F_{i'}$ is computed by adding all the terms.
$F_{i'}=F_{ext}(i)+F_{i\, s1}+F_{i\, s2}$.\\

@@

At last, we find $F'_{i'}=F_{i'}+FL_{i'}+FA_{i'}$ and apply movement
equations.

\end{itemize}
\item Dynamic of the pedestrian

The pedestrian always wants to move in the direction his FVP is pointing
and its magnitude is defined as $F_{d}$ or desire force:

@@

\end{itemize}

\subsubsection{Algorithm}

The pedestrian movement is calculated in four steps:
\begin{enumerate}
\item Calculate forces for each FVP.
\item Update positions for each FVP.
\item Calculate forces for each pedestrian.
\item Update positions for each pedestrian.
\end{enumerate}

@@

\begin{table}[H]
\centering{}{\scriptsize{}}%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline 
{\scriptsize{}Values} & {\scriptsize{}1} & {\scriptsize{}2} & {\scriptsize{}3} & {\scriptsize{}4} & {\scriptsize{}5} & {\scriptsize{}6}\tabularnewline
\hline 
\hline 
{\scriptsize{}$\alpha=1000,\,\beta=[0.4,\,0.5]$} & {\scriptsize{}(1.800, 0.748) } & {\scriptsize{}(34.600, 8.333) } & {\scriptsize{}(1.024, 0.016) } & {\scriptsize{}(1.910, 0.022) } & {\scriptsize{}(2.392, 0.005) } & {\scriptsize{}(111.062, 19.122)}\tabularnewline
\hline 
{\scriptsize{}$\alpha=2000,\,\beta=0.08$} & {\scriptsize{}(5.333, 2.625)} & {\scriptsize{}(12.333, 8.340) } & {\scriptsize{}(1.052, 0.003) } & {\scriptsize{}(1.876, 0.003) } & {\scriptsize{}(2.391, 0.002) } & {\scriptsize{}(106.185, 13.778)}\tabularnewline
\hline 
\end{tabular}\protect\caption{Metrics comparing SFM vs FVPM. Average of $10$ runs.}
\end{table}
